---
title: "LarriMiller_Assignment3"
author: "Larri Miller"
date: "due 11/06/2020"
output: html_document
---

# Digital Behavioral Data Assignment 3

Creating token to access Twitter API
``` {r}
library(rtweet)
mytoken <- create_token(
  app = "R_Workshop_DB",
  consumer_key = "",
  consumer_secret = "",
  access_token = "",
  access_secret = "")

```

Step 1: Collect Tweets containing #election2020 & including retweets
``` {r}
tweets <- search_tweets("#election2020", include_retweets = TRUE, n = 1000, retryonratelimit = TRUE,  token = mytoken)
```

Even though it is not required, I want to save my data frame as a CSV. This way I can reuse the same data frame without having to finish the assignment all in one go.
``` {r}
save_as_csv(tweets, "tweets_vote.csv")
```

Opening the saved CSV file 
``` {r}
tweets <- read.csv("tweets_vote.csv")
```

Step 2: Create a network from tweets
```{r}
library(devtools) #you would install this library as well
devtools::install_github("JohnCoene/twinetverse")

library(graphTweets)
library(twinetverse)

extractrt <- function(tweets){
  rt <- tweets %>% 
    gt_edges(screen_name, retweet_screen_name) %>% # get edges
    gt_nodes() %>% # get nodes
    gt_collect() # collect
  
  return(rt)
}

rtnet <- extractrt(tweets)

extractmt <- function(tweets){
  
  mt <- tweets %>% 
    gt_edges(screen_name, mentions_screen_name) %>% # get edges
    gt_nodes() %>% # get nodes
    gt_collect() # collect
  
  return(mt)
}

mtnet <- extractmt(tweets)

#define a function called nodes to extract node information from a network object

nodes <- function(net){
  
  c(edges, nodes) %<-% net
  nodes$id <- as.factor(nodes$nodes) 
  nodes$size <- nodes$n 
  nodes <- nodes2sg(nodes)
  nodes <- nodes[,2:5]
  
  return(nodes)
}

#define a function called edges to extract edge information from a network object

edges <- function(net){
  
  c(edges, nodes) %<-% net
  edges$id <- seq(1, nrow(edges))
  edges <- edges2sg(edges)
  
  return(edges)
}

#apply the two self-defined functions
rtnet_nodes <- nodes(rtnet)
rtnet_edges <- edges(rtnet)

mtnet_nodes <- nodes(mtnet)
mtnet_edges <- edges(mtnet)
```

Looking at the first two retweets on the edge list
``` {r}
library(DT)
datatable(rtnet_edges, options = list(pageLength = 2))
```

Step 3: List top users by a variety of network metrics -- convert to igraph
``` {r}
library(igraph)
# use rtnet_edges as the edgelist and rtnet_nodes as the node list. Set the network type as directed

rt <- graph_from_data_frame(d=rtnet_edges, vertices=rtnet_nodes, directed=T) 

# see edge weight by copying the values from the size column in rtnet_edges

rt <- set_edge_attr(rt, "weight", value= rtnet_edges$size)

# we do the same for the mention network

mt <- graph_from_data_frame(d=mtnet_edges, vertices=mtnet_nodes, directed=T) 
mt <- set_edge_attr(mt, "weight", value= mtnet_edges$size)
```

counting how many nodes & edges in rt
``` {r}
vcount(rt) #nodes
ecount(rt) #edges
```

checking top 5 most retweeted users
``` {r}
indegree_rt <- sort(degree(rt, mode = "in"), decreasing = TRUE)
indegree_rt[1:6]
```

checking top 5 users who are most active in retweeting others
``` {r}
outdegree_rt <- sort(degree(rt, mode = "out"), decreasing = TRUE)
outdegree_rt[1:5]
```

checking top 5 users by betweenness centrality
``` {r}
bt <- sort(betweenness(rt, directed=T, weights=NA), decreasing = TRUE)
bt[1:5]
```

Step 4: Network Visualization
``` {r}
library(visNetwork)
library(scales)

# set node size by betweenness centrality
V(rt)$size <- bt

# set node color by the cluster a node belongs to 
wc <- cluster_walktrap(rt)
V(rt)$color <- membership(wc)

# creating the 2core kcore
kcore <- coreness(rt, mode = "all")
twocore <- induced_subgraph(rt, kcore >= 2)

# visualize!
visIgraph(twocore, idToLabel = TRUE, layout = "layout_nicely") %>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)

```
